Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-07-30 edubots_surveys.Rnw
Making it use the same directory for figures or it will not find them

<<setup, echo=FALSE,message=FALSE>>=
library(ggplot2)
library(dplyr)
library(tidyr)
library(scales)
library(ggthemes)
library(tidyverse)
library(corrplot)

>>>>

<<setup, echo=FALSE,message=FALSE>>=
knitr::opts_chunk$set(fig.path='figures/')
library(ggplot2)
library(dplyr)
library(tidyr)
library(scales)
library(ggthemes)
library(tidyverse)
library(corrplot)
